Double Trouble: Understanding Sex Differences in Synthetic Lethal interactions in Human Cancers \\~\\ Project Updates

### 2023-07-15 july18meeting_pres2/may30ccgmeeting.tex
updates to ppt
updates

	\begin{frame}{Finding Differentially Expressed Genes (DESeq2)}

>>>>

	\begin{frame}{Finding Differentially Expressed Genes (DESeq2)}
		\includegraphics[width=12cm, height=8cm]{all_cancersvolcano_analysis_0.9.png
		}
	\end{frame}

	\begin{frame}{Differences in Number of DE Genes Males vs Females}
		\centering \includegraphics[width=9cm, height=5cm]{all_cancersvenndiagram_malede_vs_femalede_0.9.png}
		\begin{itemize}
			\item \textcolor{blue}{MALES: 358 up-regulated in tumor, 280 Down-regulated in tumor}
			\item \textcolor{yellow}{FEMALES: 171 up-regulated in tumor, 70 down-regulated in tumor}
		\end{itemize}
	\end{frame}

	\begin{frame}{Enriched Biological Processes Differ in Males and Females}
		\includegraphics[width=12cm, height=8cm]{all_cancersgsea_exclusivedegenes_male_female_bp0.9.png}
	\end{frame}

	\begin{frame}
		content...
	\end{frame}
